# Flextable

```{r}
library(flextable)
library(magrittr)
```

```{r load_data_airquality}
data <- airquality
```


## Introduction to Flextable
Another alternative to create a beautiful tables. It can produce nice tables in Word, PowerPoint or HTML.

#### Extensive formatting capabilities

* Flexible and Rich Syntax
* Can be Mixed with text, images, ggplot and hyperlinks

#### Publication Quality

* Support for Caption and cross-references in HTML, Word, and PDF
* Everything is coded
* Already used by big companies

#### Statics Table

#### Variety of Supported Outputs
Output includes HTML5, Ms Word, Ms PowerPoint and PDF

#### Detailed Documentation
Documentation available online at : https://ardata-fr.github.io/flextable-book/
Detailed tutorial available by the author in youtube  at : https://www.youtube.com/watch?v=-EuPFZCTnHE&t=53s

### A First Example

```{r}
flextable(data[ sample.int(5),]) %>%
  add_header_row(colwidths = c(4,2), values = c("Air Quality", "Time")) %>%
  theme_vanilla() %>%
  add_footer_lines("Daily measurements in New York, May to September 1973") %>%
  color(part = "footer", color = "#666666") %>%
  set_caption(caption = "New York Air Quality Measurements")
```

### How to select the row and column

Used "col_keys = " to select certain columns, add empty columns if it is not present in the data

```{r}
data_short <- head(data, n = 5)
flextable(data_short,
  col_keys = c("Wind", "Temp", "Month")) %>%
  add_header_row(colwidths = c(2,1), values = c("Air Quality", "Time")) %>%
  theme_vanilla() %>%
  add_footer_lines("Daily measurements in New York, May to September 1973") %>%
  color(part = "footer", color = "#666666") %>%
  set_caption(caption = "New York Air Quality Measurements")
```

### Selectors

i select the rows, while j select the column.
We can select certain row and column by expressing a formula, as character vector, integer vector or logical vector.

Example of making the wind and temp data turned orange when the corresponding wind value < 10.

```{r}
data_short <- head(data, n = 5)
flextable(data_short,
  col_keys = c("Wind", "Temp", "Month")) %>%
  add_header_row(colwidths = c(2,1), values = c("Air Quality", "Time")) %>%
  theme_vanilla() %>%
  add_footer_lines("Daily measurements in New York, May to September 1973") %>%
  color(part = "footer", color = "#666666") %>%
  set_caption(caption = "New York Air Quality Measurements") %>%
  color(i = ~ Wind < 10, j = c("Wind", "Temp"), color = "orange") %>% #change color
  bg(i = ~ Temp >70, j = "Temp", bg = "red") #change background 
```

### Parts of the table
there are only three parts: header, body and footer.

#### Header

Header default to only showing a column names

#### Body

Body default only showing the cells.

#### Footer

Footer is non-existent by default, otherwise it should be specified.

Here the example of selecting each parts.
```{r}
data_short <- head(data, n = 5) #selecting few rows of the data
flextable(data_short,
  col_keys = c("Wind", "Temp", "Month")) %>%   # selecting the column to be displayed
  add_header_row(colwidths = c(2,1), values = c("Air Quality", "Time")) %>%  #specify the additional header
  theme_vanilla() %>%  # selecting the theme
  add_footer_lines("Daily measurements in New York, May to September 1973") %>% #specifying the footer
  color(part = "footer", color = "#666666") %>% # selecting footer colour
  set_caption(caption = "New York Air Quality Measurements") %>% #add caption in the footer
  color(i = ~ Wind < 10, j = c("Wind", "Temp"), color = "orange") %>% #change color
  bg(i = ~ Temp >70, j = "Temp", bg = "red") %>% #change background 
  bg(part = "header", bg = "light blue")    # add background color to header
```

#### Cell content

content of a cell are following the data frame by default, but it can be customized.

colformat_double : to define how to display "doubles"
colformat_int : to define how to display "integers"
colformat_char : to define how to display "characters"

additionally also there are colformat for others, including colformat_datetime(), colformat_date(), colformat_image(), colformat_lgl(), and colformat_num().

with multiple content we can select with i and j and parts.




















